\pkg{DNest4}: Diffusive Nested Sampling in \proglang{C++} and \proglang{Python}

### 2016-05-31 paper/ms.tex
Nicer pgm and notation (no bold)

If $N$ is the number of components, $\boldsymbol{x}_i$ is the parameters
of the $i$th component, and $\alpha$ is the hyperparameters, the prior
can be factorised via the product rule, giving
\begin{align}
p\left(N, \alpha, \left\{\boldsymbol{x}_i\right\}_{i=1}^N\right)
&= p(N)p(\alpha | N)p\left(\left\{\boldsymbol{x}_i\right\}_{i=1}^N | \alpha, N\right).
\end{align}
The specific assumptions of \pkg{RJObject} are that this simplifies to
\begin{align}
p\left(N, \alpha, \left\{\boldsymbol{x}_i\right\}_{i=1}^N\right)
&= p(N)p(\alpha)
\prod_{i=1}^N
p\left(\boldsymbol{x}_i | \alpha\right).
\end{align}
That is, the prior for the hyperparameters is independent of the number of
components, and each component is independent given the hyperparameters.
A probabilistic graphical model (PGM) is shown in Figure~\ref{fig:rjobject_pgm}.

\begin{figure}[ht!]
\begin{center}
\includegraphics[width=0.4\textwidth]{figures/rjobject_pgm.pdf}
\caption{A PGM created using Daft ({\tt http://daft-pgm.org}).\label{fig:rjobject_pgm}}
\end{center}
\end{figure}

>>>>

If $N$ is the number of components, $x_i$ denotes the vector of parameters
of the $i$th component, and $\alpha$ is the vector of hyperparameters, the prior
can be factorised via the product rule, giving
\begin{align}
p\left(N, \alpha, \left\{x_i\right\}_{i=1}^N\right)
&= p(N)p(\alpha | N)p\left(\left\{x_i\right\}_{i=1}^N | \alpha, N\right).
\end{align}
The specific assumptions of \pkg{RJObject} are that this simplifies to
\begin{align}
p\left(N, \alpha, \left\{x_i\right\}_{i=1}^N\right)
&= p(N)p(\alpha)
\prod_{i=1}^N
p\left(x_i | \alpha\right).
\end{align}
That is, the prior for the hyperparameters is independent of the number of
components, and each component is independent and identically
distributed given the hyperparameters.
A probabilistic graphical model (PGM) is shown in Figure~\ref{fig:rjobject_pgm}.

\begin{figure}[ht!]
\begin{center}
\hspace*{-2cm}\includegraphics[width=0.4\textwidth]{figures/rjobject_pgm.pdf}
\caption{A PGM showing the kind of prior information the \code{RJObject}
template class expresses.
Figure created using Daft ({\tt http://daft-pgm.org}).\label{fig:rjobject_pgm}}
\end{center}
\end{figure}
